We wish to model a floating spar wind turbine which is moored by three taut mooring lines equiangularly secured to the seabed of depth $h$.
Imagining the turbine interacting with the wind whilst neglecting the mooring lines, the net force acting in the direction coinciding with one of the mooring lines, as is shown in figure \ref{fig:topdown}, the two other mooring lines will resist this motion.
We assume a very simple system, where we imagine the mooring lines being made of a fiber that can be assumed to deform elastically like a spring, with a spring constant
\[
    k = \frac{\youngsmodulus A}{L}\cos{\alpha},
\]
where $\alpha$ is the angle between the mooring line and plane water surface.
\begin{Figure}
    \centering
    \captionsetup{type = figure}
    \input{topdown.tex}
    \caption{Top-down view of wind mooring system.}
    \label{fig:topdown}
\end{Figure}
\noindent
The net force acting in the direction of that one mooring line will induce a reactionary in the two others, inversely proportional to the cosine of the half angle between them.
Since the three mooring lines are distributed evenly, this half angle must be $\sfrac{\pi}{3}$, whose cosine is $\sfrac{1}{2}$.
The inverse proportionality is due to the trigonometry of the problem---the mooring line is the hypotenuse of a right triangle in which the net force is the adjacent side length.
Thus the effective spring constant is twice that of the value above, considering the horizontal contribution only.
The resulting resistance from the mooring line will also have to account for the decline at which it works in the transversal direction, yielding another cosine term.
Finally, the spring constant for the system in the horizontal direction is given by
\[
    k_{\textsc{h}} = \frac{2 \youngsmodulus A}{L} \cos^2{\alpha}, \qquad \alpha = \arcsin{(\sfrac{h}{L})}.
\]
\begin{Figure}
    \centering
    \captionsetup{type = figure}
    \input{system.tex}
    \caption{Side view.}
    \label{fig:side}
\end{Figure}
From the theory of differential equations, we know the period of such an oscillation will be
\[
    T = 2\pi \sqrt{\frac{m + m_{11}}{k_{\textsc{h}}}}, \qquad m_{11} = m,
\]
where $m$ is the mass of the tower, and $m_{11}$ is its added mass.
The spar we use here floats in the water, meaning the displaced volume of water must weigh the same as the tower, whence the added mass.

We now imagine some wave field producing heave motions in the tower.
From the previous assignment we saw that the restoring forces for heave result in a coefficient $\varrho\gravity S$, where $S$ is the water line area.
The resulting spring coefficient will then be the sum of this restoring force coefficient and three times the sine of the mooring line spring coefficient,
\[
    k_{\textsc{v}} = \frac{3 \youngsmodulus A}{L}\cos{\alpha}\sin{\alpha} + \varrho\gravity S.
\]
The factor three here comes from the three mooring lines being spaced equiangularly.

For the determination of the vertical added mass we may assume the tower to be a circular disk whose normal vector coincides with that of the heave.
We may do this as the added mass is not concerned with the surfaces orthogonal to its mode, meaning the cylindrical shell will not contribute to the added mass.
This is a simplification, as we suspect the conal shape of the spar may contribute to the added mass.
Either way, the period will be given in a similar manner as in surge, with the added mass of such a disk, halved, as we only consider half the disk,\footnote{\cite{irrotational1967kennard} \textsc{Kennard}, p.393}
\[
    T = 2\pi \sqrt{\frac{m + m_{22}}{k_{\textsc{v}}}}, \qquad m_{22} = \frac{2 \pi {r_2}^3}{3},
\]
where $r_2$ is the bottom radius of the spar.
